From Topics to Opinions: \\Modelling Subjectivity for Retweeting Analysis on Twitter

### 2014-02-04 retweet_aaai.tex
version3

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{multirow}
\newtheorem{definition}{Definition}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{From Interests to Opinions: \\Modelling Subjectivity for Retweeting Analysis}
\author{Songxian Xie, Jintao Tang \and Ting Wang\\
School of Computer, National University of Defense Technology, Changsha, P.R. China\\
\AND Ruili Wang\\
School of Engineering and Advanced Technology, Massey University, Auckland, New Zealand\\
\AND Kewen Wang\\
School of Information and Communication Technology, Griffith University, Brisbane, QLD 4111 Australia\\
}
\maketitle
\begin{abstract}
\begin{quote}
Social media such as Twitter provides researchers with abundant User-Generated Content (UGC) for analyzing users' online behaviors.  In this paper, we focus on retweeting behavior, which is one of the key mechanisms of information dissemination on Twitter. 
User modelling has been proved to be effective in previous researches. However few studies have investigated the subjectivity of users. 
Motivated by psychological researches, we propose a novel subjectivity model by combining both topic-of-interests and opinions articulated in UGC. 
We also define a novel weighting function to measure the subjectivity similarity, and demonstrate that a user is more likely to retweet a message because of approximate subjectivity similarity.  
In the experiments, the subjectivity similarity is verified to be correlated with retweeting behavior by means of ANOVA test. 
When comparing with other topic-based models in retweeting prediction, our model outperforms other models with best accuracy. Our model gives significant accuracy improvement over an off-the-shelf predicting model considering other factors.
\end{quote}
\end{abstract}

\section{Introduction}
\label{introduction}
\noindent Microblogging has become a center of attention in the area of social networking due to the amount of users it has attracted and the volume of messages it produces daily. 
Microblogging services such as Twitter appear to play an important role in the process of information dissemination on the Internet, making it possible for messages to spread virally in a matter of minutes. 
The retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message (i.e. tweet). 
Actually almost a quarter of the tweets are retweeted from other users \cite{yang2010understanding}. 
Understanding how retweeting behavior works can help explaining information dissemination on Twitter.

There have been many studies trying to identify factors that influence whether a tweet will be retweeted \cite{boyd2010tweet,kwak2010twitter}. However few studies have investigated the subjective motivation of a user to retweet a message. 
The subjective initiative nature of human determines that his behavior pattern is subjectivity driven. Psychological researchers have identified subjectivity as the underlying factor that influences human's behaviors \cite{moore2008awareness}. 
Also according to theory of \textbf{Biased Assimilation}, people tend to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
Users receive thousands of tweets on different topics every day, whether a tweet will be retweeted will depend on the subjective choice of users. 
From the point of a user, retweeting is a process that includes reading the tweet, evaluating the content and deciding whether to share. The crucial part is to evaluate whether a tweet contains information interesting to the user who might find that it is worthy to be shared.  
Therefore modelling the subjective motivation of users will provide an important perspective for retweeting behavior analysis. 
This research is motivated by a desire to find what drives the subjective users of social networks to disseminate information they come across.

Previous studies on retweeting analysis have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{macskassy2011people,feng2013retweet}. 
Specifically, researchers have tried to model users from four types of information:
profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Whom you connect}") \cite{pennacchiotti2011machine}. 
Especially topics encapsulated in rich linguistic content of a user have been proved consistently dependable for behavior analysis \cite{petrovic2011rt}. However no studies have considered how to model the subjective aspect (``\textbf{what's your opinions}") when modelling a user.  In this paper, we propose a novel method to model sujectivity of a user(we name it subjectivity model) by combining both the topics and opinions.

Social media is a platform where different opinions are presented by allowing users gennerate contents on topics they are interested in. 
The subjectivity of a user is encoded in the User-Generated Content (UGC) on Twitter. 
Therefore, we explore the tweets a user has published to establish the subjectivity model. 
For the retweeting analysis problem, we assume the probability a user retweets a message could be evaluated with subjectivity similarity measurement. 
We design a novel weighting function to measure the subjectivity similarity, and propose three subjectivity similarities among a tweet, its author and followers to analyze the motivation of retweeting behaviors. 
Expertiments on Twitter dataset show that retweeting behaviors are correlated with all three subjectivity similarities, our subjectivity model outperforms topic-based user model for retweeting prediction, and the subjectivity similarities significantly improve the performance of an off-the-shelf predicting model considering other factors.

The rest of the paper is organized as follows: we give the definition and establishment details of the proposed subjectivity model in the next section, and in section 3 the subjectivity similarity is defined and specified for the retweeting analysis problem, experiments of quantitative evaluation is carried out in section 4, the related works are described in section 5 and Section 6 summarizes the paper and points out future work.

@@

Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historic behaviors and remarks \cite{engbert2007agency}. 
Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their linguistic contents \cite{stein2005subjectivity}. 
How to computationally model the subjectivity of a user is still a challenging problem. 
The advent of online social media such as Twitter has given a new layout to the challenge.  
Twitter allows users to show their personal subjectivity by publishing short messages, which provides researchers with data resources to model the subjectivity of users.
First of all, we give a formal definition of the subjectivity model under the context of Twitter.

@@

Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of following relationships between users. For each user $ u \in V $, there is a tweets collection $ M_{u} $ denotes his message history. We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ to evaluate their opinions towards these topics. 
For the ``subjectivity'' of a user $ u  \in V $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
\begin{definition}[Subjectivity Model]
The subjectivity model $ P \left( u \right) $ of user $ u $, is the combination of topics $\left\lbrace  t_{i} \right\rbrace $ the user talks about in topic space $T$ and the user's opinions ${o_{i}}$ towards each topic evaluated in sentiment valence space $ O $. 
\begin{equation}
\label{usermodel}
P \left( u \right) = \lbrace \left( t_{i}, w_{u} \left( t_{i} \right), d_{u,t_{i}} \left( o_{i} \right) \right) \,\vert  t_{i} \in T, \, o_{i} \in O \rbrace
\end{equation}
where:
\begin{itemize}
\item with respect to user $ u $, for each topic $t_{i} \in T$, its weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, subject to $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
\item opinion of the user towards topic $t_{i}$ is modelled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
\end{itemize}
\end{definition}
Figure~\ref{fig0} is a visualized subjectivity model of a user in a $ [0,100] $ topics space and a $ [0,8] $ sentiment valence space. 
\begin{figure}[htb]
%\centering
\includegraphics[width=3.8in,height=2.0in]{fig1.pdf}
\caption{The left subgraph denotes two topics a user tweets about with weights $ \left( w_{u}\left( t_{23} \right)=0.43, w_{u}\left( t_{86} \right)=0.57\right)  $. the right subgraph denotes opinions towards two topics: for topic 23, $ ( d_{u,t_{23}} \left( o_{2} \right)=0.1, d_{u,t_{23}} \left( o_{4} \right)=0.5,d_{u,t_{23}} \left( o_{5} \right)=0.3,d_{u,t_{23}} \left( o_{6} \right)=0.1) $; for topic 86, $ \left( d_{u,t_{86}} \left( o_{4} \right)=0.66, d_{u,t_{86}} \left( o_{5} \right)=0.34 \right) $.}
\label{fig0}
\end{figure}

@@

The definition of a subjectivity model is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from the message histories of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$

@@

Topic analysis for all users in a global network on Twitter is a nontrivial task. 
There are millions of users and billions of tweets associated with these users. The effectiveness and efficiency of the topic analysis algorithm is a big problem.
However, the ``follow'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily'', which has been observed in many social networks \cite{mcpherson2001birds}.
Homophily implies that a user follows another user because of sharing common interests. 
According to the principle of homophily, we put forwards the concept of \textbf{Local Topic Space} by combining topic analysis and network topology on Twitter: 
\begin{definition}[Local Topic Space]
\label{local}
Let $G=\left( V,E \right) $ denotes global social network, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
to denote $ u $'s $ \tau $-ego network, where $ \tau $-ego network means subnetwork formed by $ u $'s $ \tau $-hop 
friends in the network $ G $, and $ \tau \geqslant 1 $ is a tunable integer parameter to control the scale of the ego network. 
In the $ \tau $-ego network of $ u $, all users concentrate on limited topics derived from the content generated by them, and these topics form a local topic space $ T_{u} $.
\end{definition}

Previous studies have tried to identify topics from tweets by finding key words \cite{chen2010short}, extracting  entities \cite{abel2011analyzing} or linking tweets to external knowledge categories \cite{macskassy2011people}. Works also show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} are more effective in identifying topics from short and informal social media language \cite{hong2010empirical}, so we adopt the user-level LDA model for topic analysis. 
However, the LDA model is adapted to our local topic space assumption, and the relatively tiny size and topic homophily of an ego network lower the impact of data sparsity and degrade the calculation complexity of LDA.

@@

In the Natural Language Processing area, opinion mining or sentiment analysis is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}. Opinions are often regulated as sequential discrete values to represent sentiment strength (for example: 0 stands for negative and 1 for positive). Sentiment analysis researches have dived into the social media language and provided effective sentiment analysis tools \cite{thelwall2010sentiment,hu2013unsupervised}. In this work,we just make use of the off-the-shelf work of sentiment analysis.
The SentiStrength package has been built to cope with sentiment analysis in short informal text of social media \cite{thelwall2010sentiment}. 
It assigns two values to each tweet standing for sentiment strengths: a positive and a negative sentiment measurement, with $ \left[ -5,-1 \right]  $ denoting negative and $ \left[ 1,5 \right]  $ denoting positive sentiment strength, which can be used to catch fine opinion distributions in a user's subjectivity model.  
For the convenience of distribution calculation, we map the output of SentiStrength to a single value in sentiment valence space $ \left[ 0, 8 \right] $ as follows:
\begin{equation}
\label{opinionmap}
o= \left\{ 
\begin{array}{lll}
{p+3} & if \vert p \vert > \vert n \vert \\
{n+5} & \text{if } \vert n \vert > \vert p \vert \\
{4}  & \text{if } \vert p \vert = \vert n \vert
\end{array}
\right.
\end{equation}
where $ p $ denotes the positive sentiment strength and $ n $ denotes negative sentiment strength.

@@

As Definition~\ref{local} describes, a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $ for a user $ u $ can be extracted from global network. 
Then the subjectivity model of each user $ u \in G_{u} $ can be concreted within the ego network. 
$ M_{u}=\left\lbrace m_{i} \vert i \in \left[ 1, \cdots, N \right]  \right\rbrace$ denotes tweets set published by user $ u $. A Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ can be constructed using LDA topic model with a single document representing all concatenated tweets in $ M_{u} $.
The topic model is built with the parameter $ \theta_{u} $\ representing the distribution of user $ u $ over topics he talks about. Simultaneously SentiStrength is applied to each tweet $ m \in M_{u} $ and outputs sentiment strength $ s_{m} $. 
subjectivity model of user $ u $ is built as follows:
\begin{itemize}
\item Firstly, the corresponding parameter $ \theta_{u} $ of topic model for user $ u $ can be regarded as his topic distribution in the Local Topic Space $ T_{u} $, and the topics he talks about are $ Z_{u}= \left\lbrace z \vert p\left( z \vert \theta_{u}\left( z \right)  \right)>0 \right\rbrace $.
\item Secondly, the topic model is applied to each tweet $ m $ to identify topics it talks about, denoted as $ Z_{m} =\left\lbrace z_{m} \vert p\left( z_{m} \vert \theta, \beta, Z_{u} \right)>0 \right\rbrace $.
\item Thirdly, the opinion distribution of user $ u $ towards topic $ t \in Z_{u} $ could be calculated as: 
\begin{equation}
\label{opinionall}
d_{u,t}\left( o \right) = \left\lbrace \dfrac{N_{o}}{\sum_{o \in O} N_{o}} \vert O=\left[ 0,8 \right] \right\rbrace 
\end{equation}
where $ N_{o} $ is the number of times user $ u $ expresses an opinion towards topic $ t $ with sentiment strength $ o $, which could be calculated as:
\begin{equation}
\label{opinion1}
N_{o}=\sum_{m \in Mu} I\left( s_{m} \right) , \text{ if } s_{m}=o \& t \in Z_{m}
\end{equation}
\begin{equation}
\label{opinion2}
I\left( s_{m} \right)=\left\{
\begin{array}{ll}
{1} & \text{if } s_{m}=o \& t \in Z_{m}\\
{0} & \text{else}
\end{array}
\right.
\end{equation}
For simplicity, it is postulated that the sentiment of each tweet $ s_{m} $ is related to all topics it talks about in $ Z_{m} $. As a future work, we will adopt more sophisticated method to identify opinion towards each topic in a tweet.
\end{itemize}

@@

Many factors have been proved to affect retweeting behavior \cite{suh2010want,macskassy2011people,comarela2012understanding}, however few researches have investigated the subjective motivation of a user to retweet a message. 
Apart from the context constraints, a tweet is more likely to be retweeted by a user who find its content worth to. 
Therefore, we are not interested in modelling the tweet by itself as other researches \cite{naveed2011searching,pfitzner2012emotional}, but the underlying reasons why a user want to disseminate it based on his subjective initiative. 
We assume that if a tweet is published, all followers of its author will receive it in time, and followers are likely to retweet it if they find it worthwhile. 
Under such assumption, we investigate the retweeting problem within a 1-ego network for the author of target tweets. 
In the ego network, the relation among the tweet, its author and followers can be illustrated as Figure~\ref{fig1}.
\begin{figure}[htb]
%\setlength{\belowcaptionskip}{-0.2cm} 
\centering
\includegraphics[width=1.8in,height=1.6in]{ego.pdf}
%\vspace{-4em}
\caption{Illustration of relations among tweet, author and followers. Author is denoted as $ u_{a} $, tweet as $ m $, followers as $ f_{i} $ and tweets of follower $ f_{i} $ as $ m_{i} $. An directed edge $ \left( f_{i},u_{a} \right)  $ means that $ f_{i} $ is exposed to the messages published by $ u_{a} $.}
\label{fig1}
\end{figure}

@@

The retweeting analysis problem can be formulated as follows:
For each target tweet $ m $, let $ F $ denotes the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denotes a tweet collection $ u $ has published. 
For each follower $ u_{f} \in F $, we can define a quadruple $ <u_{f}, u_{a}, m, r_{f}>  $: 
\begin{itemize}
\item $ r_{f} $ is a binary label indicating whether $ m $ is retweeted by $ u_{f} $.
\item Firstly our work focuses on building subjectivity model $ P\left( u \right)  $ for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace $ in the ego network with all tweets collections $ M=\left\lbrace M_{u} | u \in F \cup \left\lbrace u_{a} \right\rbrace  \right\rbrace  $.
\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjectivity similarities between tweet $ m $, its author $ u_{a} $ and follower $ u_{f} $. 
\end{itemize}

@@

We assume that if the tweet content and the subjectivity of a user are similar enough in terms of topics and opinions, the user will have a very high probability to adopt retweeting behavior. 
With the subjectivity models estabilshed for the author and followers, the subjective decision-making procedure can be simulated by calculating the subjectivity similarity between the tweet and users. 
In this section, we define a novel similarity measurement to quantify the subjectivity similarity, which can be divided into topic similarity and opinion similarity. 
For the calculating convenience, the tweet $ m $ is analyzed and a ``subjectivity model'' is established for  $ m $ according to the procedure for users. 
Thus the subjectivity similarity calculation for tweet and user is identical with subjectivity similarity calculation between users.

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{multirow}
\newtheorem{definition}{Definition}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (From Topics to Opinions: Modelling Subjectivity for Retweeting Analysis on Twitter)
/Author (Songxian Xie, Jintao Tang, Ting Wang, Ruili Wang, Kewen Wang)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{From Topics to Opinions: \\Modelling Subjectivity for Retweeting Analysis on Twitter}
%\author{Songxian Xie, Jintao Tang \and Ting Wang\\
%School of Computer, National University of Defense Technology, Changsha, P.R. China\\
%\AND Ruili Wang\\
%School of Engineering and Advanced Technology, Massey University, Auckland, New Zealand\\
%\AND Kewen Wang\\
%School of Information and Communication Technology, Griffith University, Brisbane, QLD 4111 Australia\\
%}
\nocopyright
\maketitle
\begin{abstract}
\begin{quote}
Social media such as Twitter provides researchers with abundant User-Generated Content (UGC) for analyzing users' online behaviors. In this paper, we focus on retweeting behavior, which is one of the key mechanisms of information dissemination on Twitter. 
To understand the motivation of retweeting behavior, previous studies have committed to modelling interests of users with topics derived from UGC, but few have investigated opinions of users. 
Inspired by psychological research, we propose a novel subjectivity model by combining both topics and opinions articulated in UGC. 
We also put forward a new way to measure the subjectivity similarity between two subjectivity models, and demonstrate that a user is more likely to retweet a message with approximate subjectivity similarity.  
In the experiments, the subjectivity similarity is verified to be correlated with retweeting behavior by a statistical hypothesis test. 
Comparing with other topic-based models in retweeting prediction, our model obtains the best evaluation performance in terms of accuracy. 
Furthermore the proposed model gives significant accuracy improvement over an off-the-shelf predicting model considering other factors.
\end{quote}
\end{abstract}

\section{Introduction}
\label{introduction}
\noindent Microblogging has become a center of attention in the area of social media due to the amount of users it has attracted and the volume of messages it produces. 
Microblogging services such as Twitter appear to play an important role in the process of information dissemination on the Internet, making it possible for messages to spread virally in a matter of minutes. 
The retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message (i.e. tweet). 
Actually almost a quarter of the tweets are retweeted from other users \cite{yang2010understanding}. 
Understanding how retweeting behavior works can help explaining information dissemination on Twitter.

There have been many studies trying to identify factors that influence whether a tweet will be retweeted \cite{boyd2010tweet,kwak2010twitter}. However few studies have investigated the subjective motivation of a user to retweet a message. 
The subjective initiative nature of human determines that his behavior pattern is subjectivity driven. Psychological researchers have identified subjectivity as the underlying factor that influences human's behaviors \cite{moore2008awareness}. 
Also according to theory of Biased Assimilation, people tend to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
Users receive thousands of tweets on different topics every day, whether a tweet will be retweeted will depend on the subjective choice of users. 
From the point of a user, retweeting is a process that includes reading the tweet, evaluating the content and deciding whether to share. The crucial part is to evaluate whether a tweet contains information interesting to the user who might find that it is worthy to be shared.  
Therefore modelling the subjective motivation of users will provide an important perspective for retweeting behavior analysis. 
This research is motivated by a desire to find what drives users of social media to disseminate information they come across.

Previous studies on retweeting analysis have shown that an enriched user model gives coherent and consistent explanation for retweeting analysis \cite{macskassy2011people,feng2013retweet}. 
Specifically, researchers have tried to model users from four types of information:
profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Whom you connect}") \cite{pennacchiotti2011machine}. 
Especially, interests of a user, i.e. topics encapsulated in User-Generated Content (UGC), have been proved consistently dependable for behavior analysis \cite{petrovic2011rt}. 
However, to our best knowledge, few studies have considered the subjective aspect (``\textbf{what's your opinions}") when modelling a user. 
In this paper, we propose a novel method to model subjectivity of users (defined as subjectivity model) by combining both the topics and opinions.

Users of social media usually present their opinions by gennerating subjective content on topics they are interested in. 
The subjectivity of a user is encoded in the UGC on Twitter. 
Therefore, we explore the tweets a user has published to establish the subjectivity model. 
To meet the challenges of data sparsity and computational complexity, we design an algorithm to build the subjectivity model by making use of the local network structure and homophily of social network. 
For the retweeting analysis problem, we assume that the probability a user retweets a message could be evaluated by a subjectivity similarity measurement. 
Therefore, we put forward a new way to measure the subjectivity similarity, and use three subjectivity similarities among tweets, authors and followers to predict retweeting behavior. 
Expertiment results show that retweeting behaviors are correlated with all three subjectivity similarities, the subjectivity model outperforms topic-based model for retweeting prediction, and the performance of an off-the-shelf predicting model is significantly improve by combining with our model.

The rest of the paper is organized as follows: firstly we give the definition and establishment details of the proposed subjectivity model, then the subjectivity similarity is defined and specified for the retweeting analysis problem, following are experiments of quantitative evaluation, the related works are described next, and we summarizes the paper and points out future work finally.

@@

Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historicalal behaviors and remarks \cite{engbert2007agency}. 
Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their linguistic contents \cite{stein2005subjectivity}. 
However, how to computationally model the subjectivity of a user is still an open challenge. 
The advent of online social media such as Twitter has given a new layout to the challenge.  
Twitter allows users to show their personal subjectivity by publishing short messages, which provides researchers with data resources to model the subjectivity of users.
Therefore, we give a formal definition of the subjectivity model under the context of Twitter.

@@

Let $G=\left( V,E \right) $ denote a social network on Twitter, where $ V $ is a set of users, and $ E\subset V\times V $ is a set of follow relationships between users. For each user $ u \in V $, there is a tweets collection $ M_{u} $ denoting his message history. We assume that there is a topic space $ T $ containing all topics users in $ V $ talk about, and a sentiment valence space $ S $ to evaluate their opinions towards these topics. 
For the ``subjectivity'' of a user $ u  \in V $, we refer to both topics and opinions articulated in his tweets collection $ M_{u} $.  
\begin{definition}[Subjectivity Model]
The subjectivity model $ P \left( u \right) $ of user $ u $, is the combination of topics $\left\lbrace  t \right\rbrace $ the user talks about in topic space $T$ and his opinions $\left\lbrace O_{t}\right\rbrace $ towards each topic distributed over sentiment valence space $ S $. 
\begin{equation}
\label{usermodel}
P \left( u \right) = \lbrace \left( t, w_{u} \left( t \right), \lbrace d_{u,t} \left( s \right)|s \in S \rbrace \right) |  t \in T \rbrace
\end{equation}
where:
\begin{itemize}
\item with respect to user $ u $, for each topic $t \in T$, its weight $ w_{u} \left( t \right)$ represents the distribution of the user's interests on it, subject to $ \sum_{t=1}^{|T|}w_{u} \left( t \right)=1 $.
\item opinion of the user towards topic $t$ is modelled as a topic-dependent sentiment distribution over sentiment valence space $ S $, $O_{t}=\lbrace d_{u,t} \left( s \right)|s \in S \rbrace $, subject to $ \sum_{s=1}^{|S|} d_{u,t} \left( s \right)=1$.
\end{itemize}
\end{definition}
Figure~\ref{fig0} is a visualized subjectivity model of a user in a $ [0,100] $ topic space and a $ [0,8] $ sentiment valence space. 
\begin{figure}[t]
%\centering
\includegraphics[width=3.5in,height=1.8in]{fig1.pdf}
\caption{Subjectivity model example. The left subgraph denotes interests distribution on topic 23 and 86: $ ( w_{u}\left( 23 \right)=0.43, w_{u}\left( 86 \right)=0.57)  $. The right subgraph denotes opinions towards two topics: $ O_{23}=( d_{u,23} \left( 2 \right)=0.1, d_{u,23} \left( 4 \right)=0.5,d_{u,23} \left( 5 \right)=0.3,d_{u,23} \left( 6 \right)=0.1) $, $ O_{86}=( d_{u,86} \left( 4 \right)=0.66, d_{u,86} \left( 5 \right)=0.34 ) $.}
\label{fig0}
\end{figure}

Specially, the topics and opinions of a tweet can also be represented by the subjectivity model in the form of  Equation~\ref{usermodel}. Therefore we assume that there is also a subjectivity model for a tweet, and will not differentiate it from the subjectivity model of a user in this paper.

@@

The definition of the subjectivity model is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from the message histories of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$.

@@

Topic analysis for all users in a global network on Twitter is a non-trivial task. 
There are hundreds of millions of users and billions of tweets associated with these users. The effectiveness and efficiency of the topic analysis algorithm is a challenge.
However, the follow relationship on Twitter is a strong indicator of a phenomenon called ``homophily'', which has been observed in many social networks \cite{mcpherson2001birds}.
Homophily implies that a user follows another user because of sharing common interests. 
According to the principle of homophily, we put forwards the concept of \textbf{local topic space} by combining topic analysis with network topology on Twitter: 
\begin{definition}[Local Topic Space]
\label{local}
In a global social network $G=\left( V,E \right) $, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
to denote $ u $'s $ \tau $-ego network, where $ \tau $-ego network means subnetwork formed by $ u $'s $ \tau $-hop 
friends in the network $ G $, and $ \tau \geqslant 1 $ is a tunable integer parameter to control the scale of the ego network. 
For the $ \tau $-ego network of $ u $, all users' interests are assumed concentrate on limited topics derived from their UGC, and these topics form a local topic space $ T_{u} $.
\end{definition}

Previous studies have tried to identify topics from tweets by finding key words \cite{chen2010short}, extracting  entities \cite{abel2011analyzing} or linking tweets to external knowledge categories \cite{macskassy2011people}. However, works show that topic model such as Latent Dirichlet Allocation (LDA) \cite{blei2003latent} is more effective in identifying topics from short and informal social media language \cite{hong2010empirical}. Therefore we adopt the user-level LDA model for topic analysis, which regards all tweets of a user as one document of LDA. The LDA model is adapted to our local topic space assumption, and the relatively tiny size and topic concentration of users in an ego network lower the impact of data sparsity, and degrade the computational difficulty of LDA.

@@

In the Natural Language Processing domain, opinion mining or sentiment analysis is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}. Opinions are often regulated as sequential discrete values to represent sentiment strength. Researches on the sentiment analysis of social media have provided effective techniques and tools \cite{thelwall2010sentiment,hu2013unsupervised}. In this work,we just make use of the off-the-shelf work, i.e. SentiStrength \cite{thelwall2010sentiment}. 
SentiStrength assigns two values to each tweet standing for sentiment strengths: a negative value within $ \left[ -5,-1 \right]  $ denoting negative strength, and a positive value within $ \left[ 1,5 \right]  $ denoting  positive strength. The $ \left[ -5,5 \right] $ sentiment valence space can be used to catch fine opinion distributions in the subjectivity model. 
For the convenience of calculation, we map the output of SentiStrength to a single value in sentiment valence space $ \left[ 0, 8 \right] $ as follows:
\begin{equation}
\label{opinionmap}
o= \left\{ 
\begin{array}{lll}
{p+3} & if \vert p \vert > \vert n \vert \\
{n+5} & \text{if } \vert n \vert > \vert p \vert \\
{4}  & \text{if } \vert p \vert = \vert n \vert
\end{array}
\right.
\end{equation}
where $ p $ denotes the positive strength and $ n $ denotes the negative strength.

@@

As Definition~\ref{local} describes, a $ \tau $-ego network $ G_{u}^{\tau}=\left( U,E_{u} \right)  $ for a user $ u $ can be extracted from global network. 
Then the subjectivity model of each user $ u \in U $ can be concreted within the ego network. 
Let $ M_{u}$ denote tweets collection published by user $ u $, and $ M=\lbrace M_{u} |u \in U \rbrace$ denote all tweets collections of users in $ G_{u}^{\tau} $. A topic model $P\left(\theta,\beta | M \right) $ can be constructed with user-level LDA model, of which the parameter $\theta$ reprents user-topic distribution and $\beta$ reprents topic-vocabulary distribution. All topics of the topic model form a local topic space $ T_{u} $. 
The parameter $ \theta_{u} $ represents the topic distribution of user $ u $ over $ T_{u} $. Simultaneously SentiStrength is applied to each tweet $ m \in M_{u} $ and outputs sentiment strength $ s_{m} $. 
The subjectivity model $P\left( u\right)  $ is established as follows:
\begin{itemize}
\item Step 1, the parameter $ \theta_{u} $ naturally corresponds to interests distribution of user $ u $ in the local topic space $ T_{u} $, and the topics $ u $ talks about are $ Z_{u}= \left\lbrace t \vert p\left( t \vert \theta_{u}\left( t \right)  \right)>0 , t \in T_{u}\right\rbrace $.
\item Step 2, the topic model is applied to each tweet $ m $ to identify topics it talks about, denoted as $ Z_{m} =\left\lbrace t \vert p\left( t \vert \theta, \beta \right)>0 , t \in T_{u} \right\rbrace $.
\item Step 3, the opinion distribution of user $ u $ towards topic $ t \in Z_{u} $ can be calculated as: 
\begin{equation}
\label{opinionall}
O_{t}= \left\lbrace d_{u,t}\left( o\right)= \dfrac{N_{o}}{\sum_{o \in O} N_{o}} |o \in O, O=\left[ 0,8 \right] \right\rbrace 
\end{equation}
where $ N_{o} $ is the number of times user $ u $ expresses an opinion towards topic $ t $ with sentiment strength $ o $, which can be calculated as:
\begin{equation}
\label{opinion1}
N_{o}=\sum_{m \in Mu} I\left( s_{m} \right) , \text{ if } s_{m}=o \& t \in Z_{m}
\end{equation}
\begin{equation}
\label{opinion2}
I\left( s_{m} \right)=\left\{
\begin{array}{ll}
{1} & \text{if } s_{m}=o \& t \in Z_{m}\\
{0} & \text{else}
\end{array}
\right.
\end{equation}
For simplicity, it is postulated that the sentiment of each tweet $ s_{m} $ is related to all topics it talks about in $ Z_{m} $. As a future work, we will adopt more sophisticated method to identify opinion towards each topic in a tweet.
\end{itemize}

As a special case, we can also establish a subjectivity model $ P\left( m \right)  $ for a tweet $ m $ with only step 2 and 3. Note that the opinion distribution for each topic $ t $ of the tweet is $(d_{m,t}\left( s_{m}\right)= 1.0 )$.

@@

Apart from the context constraints such as network topology, a tweet is more likely to be retweeted by a user who finds its content worth to. 
Therefore, we are not interested in modelling the tweet by itself as other researchers \cite{naveed2011searching,pfitzner2012emotional}, but understanding the underlying reasons that a user disseminates the tweet based on his subjective initiative. 
We assume that if a tweet is published by the author, all followers will read it in time. 
Under such assumption, we investigate the problem within a 1-ego network for the author of target tweet. 
In the ego network, the relations among a tweet, the author and followers are illustrated as Figure~\ref{fig1}.
\begin{figure}[htb]
%\setlength{\belowcaptionskip}{-0.2cm} 
\centering
\includegraphics[width=1.5in,height=1.1in]{ego.pdf}
%\vspace{-4em}
\caption{Illustration of relations among tweet, author and followers. Author is denoted as $ u_{a} $, tweet as $ m $, followers as $ f_{i} $ and tweets of follower $ f_{i} $ as $ m_{i} $. An directed edge $ \left( f_{i},u_{a} \right)  $ means that $ f_{i} $ is exposed to the messages published by $ u_{a} $.}
\label{fig1}
\end{figure}

@@

The retweeting analysis problem can be formulated as following:
For a target tweet $ m $, let $ F $ denote the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denote a tweet collection $ u $ has published. 
For each follower $ u \in F $, we can define a quadruple $ <u, u_{a}, m, r_{f}>  $: 
\begin{itemize}
\item $ r_{f} $ is a binary label indicating if $ m $ is retweeted by $ u $.
\item Firstly our work focuses on building subjectivity model $ P\left( u \right)  $ for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace $ in the ego network with all tweets collections $ M=\left\lbrace M_{u} | u \in F \cup \left\lbrace u_{a} \right\rbrace  \right\rbrace  $.
\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjectivity similarities between tweet $ m $, its author $ u_{a} $ and follower $ u $. 
\end{itemize}

@@

It is assumed that if a tweet is similar enough with the subjectivity of a user in terms of topics and opinions, the user will have a very high probability to decide to retweet it. 
With the subjectivity models estabilshed for the users and tweet, the subjective decision-making process can be simulated by calculating the subjectivity similarity between the tweet and users. 
In this section, we define a novel similarity measurement to quantify the subjectivity similarity, which consists of topic similarity and opinion similarity.
